Kung Faux Pandas \\ \large Simplifying privacy protection

### 2018-11-07 paper/amia.tex
Auto Update from local Sharelatex

\begin{table}
   \caption{Included Data Synthesis Methods}
   \label{included-methods}
   \centering
   \begin{tabular}{p{12em} l p{20em}}
     \toprule
     Method                                 & Source                    & Notes \\
     \midrule
     Kernel Density Estimator               & scipy.stats.gaussian\_kde & Inter-related ordinal and ratio data\\
     DataSynthesizer                        & Ping et al.               & Bayesian modeling of column relationships\\
     \bottomrule
   \end{tabular}
 \end{table}

@@

In all cases, synthetic data generation is a CPU intensive task; no parallelization has been implemented by either KFP nor the plugins used. While memory usage does increase as data size increases, at the 100000 rows seen here, memory usage peaked at around 2GB for the Python process.

>>>>

\begin{table}
   \caption{Summary of Included Data Synthesis Methods}
   \label{included-methods}
   \centering
   \begin{tabular}{p{12em} l p{20em}}
     \toprule
     Method                                 & Source                    & Notes \\
     \midrule
     %row 1 column 1
     Kernel Density Estimator; independent attribute mode
     %row 1 column 2
     & scipy.stats.gaussian\_kde
     %row 1 column 3
     & Creates a Gaussian Kernel Density Estimator using the Silverman method; fast but doesn’t maintain correlation between variables of the same observation.\\
     %row 2 column 1
     Kernel Density Estimator; corelated attribute mode
     %row 2 column 2
     & scipy.stats.gaussian\_kde
     %row 2 column 3
     & Creates a Gaussian Kernel Density Estimator across all variables per observation using a kde.factor of 0.01\\
     %row 3 column 1
     DataSynthesizer; independent attribute mode
     %row 3 column 2
     & Ping et al.
     %row 3 column 3
     & A histogram is derived for each attribute, noise is added to the histogram to achieve differential privacy, and then samples are drawn for each attribute; fast but doesn’t maintain correlation between variables of the same observation.\\
     %row 4 column 1
     DataSynthesizer; correlated attribute mode
     %row 4 column 2
     & Ping et al.
     %row 4 column 3
     & Data is generated through a differentially private Bayesian network capturing the correlation between attributes. Computationally expensive and requires larger input dataset compared to independent attribute mode.\\
     \bottomrule
   \end{tabular}
 \end{table}

@@

In all cases, synthetic data generation is a CPU intensive task; no parallelization has been implemented by either KFP nor the plugins used. While memory usage does increase as data size increases, at the 100000 rows seen here, memory usage peaked at around 4.7GB for the Python process.
